TITLE

### 2021-02-22 outputs/Paper.Rmd
update

# Discussion

>>>>

```{r read_data, include=FALSE}

setwd("~/Downloads/Git/groupproject-")

# read raw dataset from scripts, need to run survey_response _simulation first.
simulated_data<- read_csv("inputs/simulated_data.csv")

# We add a new column To distinguish the restaurant size by employees number. 
# if employees number >20 then we define it is big, otherwise it is small.
for (i in 1:nrow(simulated_data)){
  if ((simulated_data$Q8[i] == ">30") || (simulated_data$Q8[i] == "20-30")){
  simulated_data$size[i] = "Big"  
  }else {
    simulated_data$size[i] = "Small"
  }
}

treated_data<-
  filter(simulated_data, simulated_data$type == "Treated" ) # load treated data

control_data<-
  filter(simulated_data, simulated_data$type == "Control" ) # load control data
```

### Revenue distributions group by restaurant size
```{r revenue_distribution, echo=FALSE}

library(ggplot2)
# Treated group
rd1<-
  ggplot(treated_data, aes(x = treated_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 40, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_linedraw()
# Control group
rd2<-
  ggplot(control_data, aes(x = control_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 40, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_linedraw()
# combine two diagram in one graph
#install.packages("ggpubr")
library(ggpubr)
ggarrange(
  rd1, rd2, 
  ncol = 1, nrow = 2,
  heights = c(1, 1),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

```
# Discussion
